### 2021-01-04 ch03_esmvaltool/esmvaltool.tex
Added tables that summarizes changes made to the ESMValCore

>>>>

\begin{table}[t]
  \centering
  \begin{tabulary}{\columnwidth}{L L L}
    \toprule
    Type & Name & Description \\
    \midrule
    Derived variable & \emph{co2s} & Atmospheric \ac{CO2} concentration at
    surface \\
    \cmidrule(l){2-3}
    & \emph{et} & Evapotranspiration \\
    \cmidrule(l){2-3}
    & \emph{uajet} & Position of austral jet stream \\
    \midrule
    Preprocessor & Amplitude & Amplitude of periodic phenomena (\eg{} diurnal
    or seasonal cycles) \\
    \cmidrule(l){2-3}
    & Land/sea fraction weighting & Weighting of fields based on
    the land or sea fraction of the respective grid cells \\
    \cmidrule(l){2-3}
    & Trend & Calculation of linear trends (slope of ordinary least squares
    regression) \\
    \midrule
    Miscellaneous & Concatenate experiments & Added option to concatenate
    multiple experiments (\eg{} historical simulation with future scenarios) \\
    \cmidrule(l){2-3}
    & Expanded variable derivation & Simplified, cleaned and extended variable
    derivation \\
    \bottomrule
  \end{tabulary}
  \caption{Summary of features added to the \acf{ESMValCore}.}
  \label{tab:03:changes_to_esmvalcore}
\end{table}
